### 2022-09-09 tex/Benchmark/runge.tex
zalesak

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/zal_marker.pdf}
\caption{Distance from the centre as function of time for values of Courant number of  of 0.25, 0.3, 0.5, 0.75 and 1 (green, orange, blue, black and red,
respectively). R indicates the distance from the centre considering a perfect circle trajectory.}
\label{fig:runge_err}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=400px]{./Figures/zal_marker.pdf}
\caption{Distance from the centre as function of time for values of Courant number of  of 0.25, 0.3, 0.5, 0.75 and 1 (green, orange, blue, black and red,
respectively).}
\label{fig:runge_err}
\end{figure}
